\documentclass[main.tex]{subfiles}

\begin{document}
\chapter{Complex Analysis}
	\section{Analytic Functions}
	\subsection{Complex differentiation}
	We first start with the basic definition of limit for complex functions.
	\begin{definition}
		The function $f$ is said to have the limit $A$ as $x$ tends to $a$,
		\begin{equation*}
			\lim_{x\to a} f(x) = A,
		\end{equation*}
		if and only if the following is true:
		
		For every $\epsilon > 0$ there exists a real number $\delta > 0$ with the property that $\abs{f(x) - A} < \epsilon$ for all values of $X$ such that $\abs{x - a} < \delta$ and $x \neq a$.
	\end{definition}
	Note that the definition is the same to those of limit of a real function. This is possible since the absolute function admits both real and complex numbers. The well-known results concerning the limit of a sum, a product and a quotient of limits is preserved.
	
	Note that we also have the following properties:
	\begin{enumerate}
		\item $\lim_{x \to a} \overline{f(x)} = \overline{A}$.
		\item $\lim_{x \to a} \Re f(x) = \Re A$.
		\item $\lim_{x \to a} \Im f(x) = \Im A$.
	\end{enumerate}
	\begin{definition}
		The function $f$ is said to be continuous if $\lim_{x \to a} f(x) = f(a)$.
	\end{definition}
	\begin{definition}
		A complex-valued function $f$ defined on an \textit{open} subset $G$ of $\CC$ is differentiable at $z\in G$ if
		\begin{equation*}
			\lim_{h\to 0} \frac{f(z + h) - f(z)}{h}
		\end{equation*}
		exists. When the limit does exist it is denoted by $f'(z)$.
	\end{definition}

	 Let us consider when $f$ is a real function, that is $f(z)$ is real for all value of $z$. 
	\begin{theorem}
		A real function of a complex variable has the derivative zero, or else does not exists.
	\end{theorem}
\begin{proof}
	Suppose the derivative $f'(z)$ exists.
	Then the quotient
		\begin{equation*}
		\frac{f(z + h) - f(z)}{h}
		\end{equation*}
		is real if $h$ is real; and if $h = ia$ is purely imaginary, then
		\begin{equation*}
		\frac{f(z + ia) - f(z)}{ia}
		\end{equation*}
		is imaginary. It follows that $f'(z) = 0$ for all $z$ in the domain. Thus a real function of a complex variable must either has the derivative zero, else the derivative does not exist.
\end{proof}
	
	\subsection{Conformal mappings}
	
	\section{Contour Integration and Cauchy's theorem}
		\subsection{Maximum modulus theorem}
	\section{Expansions and singularities}
		
	\section{The residue theorem}
		\begin{theorem}[Rouch\'{e}'s theorem]
			Let $f$ and $g$ be holomorphic inside and on a contour $\gamma$ and suppose that $\abs{f(z)} > \abs{g(z)}$ on $\gamma^\ast$. Then $f$ and $f + g$ have the same number of zeros inside $\gamma$.
		\end{theorem}
	
	\subsection{Open mapping theorem}
		
\end{document}